---
title: "p8105_hw5_bpg2118"
author: "Benjamin Goebel"
date: "11/18/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
```

## Problem 1

Let's begin by reading in the data.
```{r message=FALSE}
# Read in the homicide data
homicide_data <- read_csv(here("data", "homicide-data.csv"))
```
There are `r nrow(homicide_data)` rows and `r ncol(homicide_data)` columns.

Let's add a city_state column.
```{r}
# Add city_state column
homicide_data <- homicide_data %>%
  mutate(city_state = str_c(city, ", ", state))
```

Now, we can summarize the total number of homicides and unsolved homicides in 
each city, state.
```{r}
# Summarize total number of homicides and unsolved homicides in each city, state
# Unsolved homicide: disposition == Closed without arrest | disposition ==
#                    Open/No arrest.
city_state_summary_homicides <- homicide_data %>%
  group_by(city_state) %>%
  summarize(
    n_unsolved_homicides = sum(disposition == "Closed without arrest" |
                               disposition == "Open/No arrest"),
    n_homicides = n()
  )
```

As requested, we can estimate the proportion of unsolved homicides in 
Baltimore, MD.
```{r}
# Get Baltimore summary homicides and then estimate proportion of unsolved
# homicides
baltimore_summary_homicides <- city_state_summary_homicides %>%
  filter(city_state == "Baltimore, MD")
baltimore_prop_test <- prop.test(pull(baltimore_summary_homicides, n_unsolved_homicides),
          pull(baltimore_summary_homicides, n_homicides))
```

Next, we can tidy the output from the prop test and view the proportion 
estimate, as well as the lower and upper bounds of the confidence interval.

```{r}
# Tidy Baltimore prop test
# Get proportion estimate and lower and upper bounds of the confidence interval
broom::tidy(baltimore_prop_test) %>%
  select(estimate, conf.low, conf.high) %>%
  knitr::kable()
```
Now, we can get the proportion estimate and lower and upper bounds for each
city.

```{r warning=FALSE}
# Create a prop test function to apply to any SUMMARIZED city df
city_prop_test_fun <- function(city_df) {
  return(prop.test(pull(city_df, n_unsolved_homicides), 
                   pull(city_df, n_homicides)))
}

# Nest homicide data
# Map prop test to each city homicide data
# Map tidy to each prop test
# Select columns
city_state_prop_test <- city_state_summary_homicides %>%
  nest(data = n_unsolved_homicides:n_homicides) %>%
  mutate(
    test_results = map(data, city_prop_test_fun),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, conf.low, conf.high)
```
Next, we will create a plot that shows the proportion estimates with 
confidence intervals for each city.

```{r}
# Plot proportion estimate of unsolved homicides for 50 large U.S. cities
# Use geom_errorbar to plot confidence intervals
city_state_prop_test %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme_bw() +
  labs(
    x = "U.S. City",
    y = "Proportion Estimate of Unsolved Homicides",
    title = "Proportion Estimate of Unsolved Homicides for 50 Large U.S. Cities"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
        plot.title = element_text(hjust = 0.5))
  
```

## Problem 2

Let's do the following:
*   Create a data frame with one column being a list of file names and a
second column being a list column of data frames with each data frame being
the corresponding read-in data from the file name.
*   Unnest the list column of data frames.  
*   Pivot the data so that week is in one column and the week measurement is in
another column.  
*   Create patient ID and treatment variables, as well as, a variable that
combines the patient ID and treatment to uniquely identify each patient.

```{r message=FALSE}
# Create a data frame with a list of file names and list of patient data frames
# Get list of data frames by iterating over file names list and read_csv
# Unnest list column
# Pivot to get week in one column and week measurement in another
# Create patient ID and treatment variables and create a variable of the
# combination of the two to uniquely identify each patient.
longitudinal_df <- tibble(
  file_names = list.files(here("data", "problem_two_longitudinal_data")),
  patient_data = map(.x = file_names, 
                     ~read_csv(here("data", 
                                   "problem_two_longitudinal_data", .x)
                              )
                     )
) %>%
  unnest(patient_data) %>%
  pivot_longer(starts_with("week"),
               names_to = "week",
               names_prefix = "week_",
               values_to = "week_results") %>%
  separate(file_names, c("treatment_type", "patient_id"), sep = "_") %>%
  mutate(patient_id = str_replace(patient_id, ".csv", ""),
         treatment_type_patient_id = str_c(treatment_type, patient_id),
         week = as.integer(week),
         treatment_type = str_replace(treatment_type, "con", "control"),
         treatment_type = str_replace(treatment_type, "exp", "experimental"))
```
Now, that we have the data in a tidy format, let's plot week measurements by
week for each subject in the experiment. We can color by treatment group
to compare the two treatment groups.
```{r}
# Spaghetti plot: week measurement by week for each participant colored by
# treatment group
longitudinal_df %>%
  ggplot(aes(x = week, y = week_results, group = treatment_type_patient_id,
             color = treatment_type)) +
           geom_line() +
  scale_x_continuous(breaks = 1:8) +
  theme_bw() +
  labs(
    title = "Week Measurement by Week Number for each Patient",
    x = "Week Number",
    y = "Week Measurement",
    color = "Treatment Arm"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```


